Thesis Title

### 2022-02-12 chapters/introduction.tex
Updates from Overleaf

@@

The release of the first truly high-throughput sequencing platform in the mid-2000s heralded a 50,000-fold drop in the cost of DNA sequencing in comparison with the first generation technologies and led to the denomination of next-generation sequencing (NGS) \citep{goodwin_coming_2016}. This trend has continued to throughout the next two decades of continued development and improvement, allied to the emergence of benchtop sequencing platforms with high throughput of sequencing data and turnaround times of days, making it a standard in any microbiology and public health laboratories \citep{loman_twenty_2015}, albeit with a much shorter read lengths ranging from 45 to 300 bases. Second generation sequencing methods can be grouped into two major categories: (1) sequencing by hybridisation and (2) sequencing by synthesis.

Sequencing by hybridisation

the development and commercialisation of high-throughput, massively parallel or next-generation sequencing, which democratized sequencing by offering individual laboratories access to the technology.

>>>>

The development and commercialisation of high-throughput, massively parallel sequencing, has democratised sequencing by offering individual laboratories, either in research or in health, access to the technology.

@@

The release of the first truly high-throughput sequencing platform in the mid-2000s heralded a 50,000-fold drop in the cost of DNA sequencing in comparison with the first generation technologies and led to the denomination of next-generation sequencing (NGS) \citep{goodwin_coming_2016}. This trend has continued to throughout the next two decades of continued development and improvement, allied to the emergence of benchtop sequencing platforms with high throughput of sequencing data and turnaround times of days, making it a standard in any microbiology and public health laboratories \citep{loman_twenty_2015}. Second generation sequencing methods can be grouped into two major categories: (1) sequencing by hybridisation and (2) sequencing by synthesis.

\subsubsection{Sequencing by hybridisation}

Sequencing by hybridisation, originally developed in the 1980s, relies on the binding of one strand of DNA to its complementary strand (hybridisation). By repeated hybridisation and washing cycles, it was possible to build larger contiguous sequence information, based upon overlapping information from the probe hybridisation spot, being sensitive to even single-base mismatches when the hybrid region is short or if specialised mismatch detection proteins are present \citep{slatko_overview_2018, detter_nucleic_2014}. Although widely implemented via DNA chips or microarrays, has largely been displaced by other methods, including sequencing by synthesis \citep{goodwin_coming_2016}.

\subsubsection{Sequencing by synthesis}

Sequencing by synthesis methods are further development of Sanger sequencing, without the ddNTPs terminators, in combination with repeated cycles, run in parallel, of synthesis, imaging, and methods to incorporate additional nucleotides in the growing chain. All second generation sequencing by synthesis approaches rely on a ‘library’ preparation using native or amplified DNA usually obtained though (1) DNA extraction, (2) DNA fragmentation and fragment size selection, and (3) ligation of adapters and optional barcodes to the ends of each fragment. This is generally followed by a step of DNA amplification. The resulting library is loaded on a flow cell and sequenced in massive parallel sequencing reactions \citep{giani_long_2020}
Besides having much shorter read lengths than first generation methods, with reads ranging from 45 to 300 bases, and an intrinsically higher error rate, the massively parallel sequencing of millions to billions of short DNA sequence reads allows for the obtainment of millions of accurate sequences based upon the identification of a consensus (agreement) sequences \citep{slatko_overview_2018, goodwin_coming_2016, hagemann_overview_2015}.

Many of the currently available sequencing by synthesis methods approaches have been described as cyclic array sequencing platforms, as they involve dispersal of target sequences across the surface of a two-dimensional array, followed by sequencing of those targets \citep{hagemann_overview_2015}.
